KidsAIR: manuscript tables/figures

### 2020-06-19 dustrak_data_cleaning.Rmd
new data cleaning/merging

# Join PM data with linked IDs and make new variables for spikes in PM
```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")
kids_pm <- 
  read_rds(paste0(file_path, "Output/kids_pm_new4.rds")) 
kids_linked_ids <- 
  read_rds(paste0(file_path, "Output/kids_linked_ids.rds"))

kids_pm_new5 <- kids_pm %>% 
  mutate(home_winter_id = as.character(home_winter_id)) %>% 
  select(-home, -treatment) %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id")) %>% 
  group_by(home, sampling_day) %>% 
  mutate(pm_spike_1000 = if_else(pm > 1000, "Yes", "No"),
         pm_spike_2000 = if_else(pm > 2000, "Yes", "No"),
         pm_spike_5000 = if_else(pm > 5000, "Yes", "No")) %>% 
  ungroup() %>% 
  arrange(area, home_winter_id, pm_datetime_new)
```

>>>>

# Join PM data with linked IDs and make new variables for spikes in PM
```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")
kids_pm <- 
  read_rds(paste0(file_path, "Output/kids_pm_new4.rds")) 
kids_linked_ids <- 
  read_rds(paste0(file_path, "Output/kids_linked_ids_final.rds"))

kids_pm_new5 <- kids_pm %>% 
  mutate(home_winter_id = as.character(home_winter_id)) %>% 
  select(-home, -treatment) %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id")) %>% 
  group_by(home, sampling_day) %>% 
  mutate(pm_spike_1000 = if_else(pm > 1000, "Yes", "No"),
         pm_spike_2000 = if_else(pm > 2000, "Yes", "No"),
         pm_spike_5000 = if_else(pm > 5000, "Yes", "No")) %>% 
  ungroup() %>% 
  filter(home != "WMA300") %>%  # filtering out home with sampling issues after discussion with team
  arrange(area, home_winter_id, pm_datetime_new)
```

### 2020-06-19 home_char_act_cleaning.Rmd
new data cleaning/merging

---
title: "KidsAIR home activity and characteristics cleaning"
author: "Ethan Walker"
date: "Started 13 Jan 2020, Updated 4 March 2020"
output: pdf_document
---

@@

file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")
```

# Load, format, and save home char data
```{r}
##### WMT #####
# Load data
home_char_initial_wmt <- read_csv("Input/WMT/wmt_home_char_20200113.csv")

@@

# Save as RDS
# write_rds(wmt_home_char, "Output/wmt_home_char.rds")

##### NN #####
# Load data
home_char_initial_nn <- read_xlsx("Input/NN/nn_home_char_20200113.xlsx")

@@

# Save as RDS
# write_rds(nn_home_char, "Output/nn_home_char.rds")

##### AK #####
# Load data
home_char_initial_ak <- read_xlsx("Input/AK/ak_home_char_20200113.xlsx")

@@

# Save as RDS
# write_rds(ak_home_char, "Output/ak_home_char.rds")
```

# Join home characteristic data from different areas
```{r}
wmt_home_char <- read_rds("Output/wmt_home_char.rds")
nn_home_char <- read_rds("Output/nn_home_char.rds")
ak_home_char <- read_rds("Output/ak_home_char.rds")

@@

# write_rds(kids_home_char, "Output/kids_home_char.rds")
```

# Clean up all home characteristics data
```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")
kids_home_char <- read_rds(paste0(file_path, "Output/kids_home_char.rds"))
kids_linked_ids <- read_rds(paste0(file_path, "Output/kids_linked_ids.rds"))

home_char_clean <- kids_home_char %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id")) %>% 
  # cleaning based on checking odd values with paper logs
  mutate(residents_under5 = if_else(residents_under5 == 10, 1, residents_under5),
         residents_under5 = if_else(home == "CH307" | home == "CH323", 1, residents_under5)) %>% 
  replace_with_na(replace = list(home_year_built = 0)) %>% 
  replace_with_na(replace = list(home_floors = 0)) %>% 
  replace_with_na(replace = list(home_windows = 0)) %>% 
  replace_with_na(replace = list(residents_total = 0)) %>% 
  replace_with_na(replace = list(residents_under5 = 0)) %>% 
  replace_with_na(replace = list(residents_under18 = 0)) %>% 
  replace_with_na(replace = list(home_sqft = 0)) %>% 
  mutate(home_year_built = if_else(home_year_built == 15, 2002, home_year_built),
         home_year_built = if_else(home_year_built == 874, 1980, home_year_built)) %>% 
  replace_with_na(replace = list(home_year_built = 1400)) %>% 
  mutate(home_sqft = if_else(home_sqft == 14 & home == "CH102", 360, home_sqft),
         home_sqft = if_else(home_sqft == 14 & home == "CH107", 1152, home_sqft)) %>% 
  replace_with_na(replace = list(home_sqft = 12)) %>% 
  replace_with_na(replace = list(home_sqft = 14)) %>% 
  replace_with_na(replace = list(home_sqft = 20)) %>% 
  replace_with_na(replace = list(home_sqft = 24)) %>% 
  replace_with_na(replace = list(home_sqft = 90)) %>% 
  mutate(home_furry = if_else(home_furry == 4 & home == "WMA368", 1, home_furry),
         home_furry = if_else(home_furry == 10 & home == "WMA345", 14, home_furry),
         home_furry = if_else(home == "WMA309", 3, home_furry),
         home_pets = if_else(home == "WMA309", 3, home_pets),
         home_pets = if_else(home == "WMA437", 3, home_pets),
         home_furry = if_else(home == "WMA437", 3, home_furry)) %>% 
  replace_with_na(replace = list(home_furry = 14)) %>% 
  ungroup() %>% 
  arrange(area, home, winter_id)

@@

# Load, format, and save home activity data
```{r}
##### WMT #####
# Load data
home_act_initial_wmt <- read_csv(paste0(file_path, "Input/WMT/wmt_home_activity_20200113.csv"))

@@

# Save as RDS
# write_rds(wmt_home_act, paste0(file_path, "Output/wmt_home_act.rds"))

##### NN #####
# Load data
home_act_initial_nn <- read_xlsx(paste0(file_path, "Input/NN/nn_home_activity_20200113.xlsx"))

@@

# Save as RDS
# write_rds(nn_home_act, paste0(file_path, "Output/nn_home_act.rds"))

##### AK #####
# Load data
home_act_initial_ak <- read_xlsx(paste0(file_path, "Input/AK/ak_home_activity_20200113.xlsx"))

@@

# Save as RDS
# write_rds(ak_home_act, paste0(file_path, "Output/ak_home_act.rds"))
```

@@

# Clean up all home activity data
```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")
kids_home_act <- read_rds(paste0(file_path, "Output/kids_home_act.rds"))
kids_linked_ids <- read_rds(paste0(file_path, "Output/kids_linked_ids.rds"))

home_act_clean <- kids_home_act %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id"))

>>>>

---
title: "KidsAIR home activity and characteristics cleaning"
author: "Ethan Walker"
date: "Started 13 Jan 2020, Updated 19 June 2020"
output: pdf_document
---

@@

file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")
kids_linked_ids <- read_rds(paste0(file_path, "Output/kids_linked_ids_final.rds")) 
demographics <- read_rds(paste0(file_path, "Output/demographics_final.rds")) 
```

# Load, format, and save home char data
```{r}
##### WMT #####
# Load data
home_char_initial_wmt <- read_csv(paste0(file_path, "Input/WMT/homechar.csv"), 
                                  na = c("NULL", ""))

@@

# Save as RDS
write_rds(wmt_home_char, paste0(file_path, "Output/wmt_home_char.rds"))

##### NN #####
# Load data
home_char_initial_nn <- read_csv(paste0(file_path, "Input/NN/homechar.csv"), na = c("NULL", ""))

@@

# Save as RDS
write_rds(nn_home_char, paste0(file_path, "Output/nn_home_char.rds"))

##### AK #####
# Load data
home_char_initial_ak <- read_csv(paste0(file_path, "Input/AK/homechar.csv"), na = c("NULL", ""))

@@

# Save as RDS
write_rds(ak_home_char, paste0(file_path, "Output/ak_home_char.rds"))
```

# Join home characteristic data from different areas
```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")

wmt_home_char <- read_rds(paste0(file_path, "Output/wmt_home_char.rds"))
nn_home_char <- read_rds(paste0(file_path, "Output/nn_home_char.rds"))
ak_home_char <- read_rds(paste0(file_path, "Output/ak_home_char.rds"))

@@

# write_rds(kids_home_char, paste0(file_path, "Output/kids_home_char.rds"))
```

# Clean up all home characteristics data
```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")
kids_home_char <- read_rds(paste0(file_path, "Output/kids_home_char.rds"))
kids_linked_ids <- read_rds(paste0(file_path, "Output/kids_linked_ids_final.rds"))

home_char_clean <- kids_home_char %>% 
  mutate(area = as.factor(area)) %>% 
  right_join(kids_linked_ids, by = c("area", "home_winter_id")) %>% 
  # cleaning based on checking odd values with paper logs
  mutate(residents_under5 = if_else(residents_under5 == 10, 1, residents_under5),
         residents_under5 = if_else(home == "CH307" | home == "CH323", 1, residents_under5)) %>% 
  replace_with_na(replace = list(home_year_built = 0)) %>% 
  replace_with_na(replace = list(home_floors = 0)) %>% 
  replace_with_na(replace = list(home_windows = 0)) %>% 
  replace_with_na(replace = list(residents_total = 0)) %>% 
  replace_with_na(replace = list(residents_under5 = 0)) %>% 
  replace_with_na(replace = list(residents_under18 = 0)) %>% 
  replace_with_na(replace = list(home_sqft = 0)) %>% 
  mutate(home_year_built = if_else(home_year_built == 15, 2002, home_year_built),
         home_year_built = if_else(home_year_built == 874, 1980, home_year_built)) %>% 
  replace_with_na(replace = list(home_year_built = 1400)) %>% 
  mutate(home_sqft = if_else(home_sqft == 14 & home == "CH102", 360, home_sqft),
         home_sqft = if_else(home_sqft == 14 & home == "CH107", 1152, home_sqft)) %>% 
  replace_with_na(replace = list(home_sqft = 12)) %>% 
  replace_with_na(replace = list(home_sqft = 14)) %>% 
  replace_with_na(replace = list(home_sqft = 20)) %>% 
  replace_with_na(replace = list(home_sqft = 24)) %>% 
  replace_with_na(replace = list(home_sqft = 90)) %>% 
  mutate(home_furry = if_else(home_furry == 4 & home == "WMA368", 1, home_furry),
         home_furry = if_else(home_furry == 10 & home == "WMA345", 14, home_furry),
         home_furry = if_else(home == "WMA309", 3, home_furry),
         home_pets = if_else(home == "WMA309", 3, home_pets),
         home_pets = if_else(home == "WMA437", 3, home_pets),
         home_furry = if_else(home == "WMA437", 3, home_furry)) %>% 
  replace_with_na(replace = list(home_furry = 14)) %>% 
  ungroup() %>% 
  arrange(area, home, winter_id)

summary(home_char_clean)

@@

# Load, format, and save home activity data
```{r}
##### WMT #####
# Load data
home_act_initial_wmt <- read_csv(paste0(file_path, "Input/WMT/homeactivity.csv"), na = c("NULL", ""))

@@

# Save as RDS
write_rds(wmt_home_act, paste0(file_path, "Output/wmt_home_act.rds"))

##### NN #####
# Load data
home_act_initial_nn <- read_csv(paste0(file_path, "Input/NN/homeactivity.csv"), na = c("NULL", ""))

@@

# Save as RDS
write_rds(nn_home_act, paste0(file_path, "Output/nn_home_act.rds"))

##### AK #####
# Load data
home_act_initial_ak <- read_csv(paste0(file_path, "Input/AK/homeactivity.csv"), na = c("NULL", ""))

@@

# Save as RDS
write_rds(ak_home_act, paste0(file_path, "Output/ak_home_act.rds"))
```

@@

# Clean up all home activity data
```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")
kids_home_act <- read_rds(paste0(file_path, "Output/kids_home_act.rds"))
kids_linked_ids <- read_rds(paste0(file_path, "Output/kids_linked_ids_final.rds"))

home_act_clean <- kids_home_act %>% 
  mutate(area = as.factor(area)) %>% 
  right_join(kids_linked_ids, by = c("area", "home_winter_id"))

summary(home_act_clean)

### 2020-06-19 home_child_data_cleaning.Rmd
new data cleaning/merging

## Box location: All Files > NoonGroupData > KidsAIR > 
## FINAL DATA SETS > WMT > homewinter
wmt_homewinter_initial <- read_csv(paste0(file_path, "Input/WMT/homewinter.csv"), na = "NULL") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, homeid, winterid, interventiondate, interventiontime) %>% 
  filter(winterid != 3) %>% # filter for winterid == 1 or 2. What about missing intervention date?
  mutate(home_winter_id = as.character(homewinterid),
         home_id = as.character(homeid),
         winter_id = as.character(winterid),
         intervention_date = interventiondate,
         intervention_time = interventiontime) %>% 
  select(home_winter_id, home_id, winter_id, intervention_date, intervention_time)

@@

## Box location: All Files > NoonGroupData > KidsAIR > 
## FINAL DATA SETS > Navajo > homewinter
nn_homewinter_initial <- read_csv(paste0(file_path, "Input/NN/homewinter.csv"), na = "NULL") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, homeid, winterid, interventiondate, interventiontime) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         home_id = as.character(homeid),
         winter_id = as.character(winterid),
         intervention_date = interventiondate,
         intervention_time = interventiontime) %>% 
  mutate(winter_id = as.numeric(winter_id),
         winter_id = as.character(winter_id)) %>% 
  filter(winter_id == 1 | winter_id ==2) %>% # filter for winterid == 1 or 2. What about missing intervention date?
  select(home_winter_id, home_id, winter_id, intervention_date, intervention_time)

@@

## Box location: All Files > NoonGroupData > KidsAIR > 
## FINAL DATA SETS > AK > homewinter
ak_homewinter_initial <- read_csv(paste0(file_path, "Input/AK/homewinter.csv"), na = "NULL") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, homeid, winterid, interventiondate, interventiontime) %>% 
  filter(winterid != 3) %>% # filter for winterid == 1 or 2. What about missing intervention date?
  mutate(home_winter_id = as.character(homewinterid),
         home_id = as.character(homeid),
         winter_id = as.character(winterid),
         intervention_date = interventiondate,
         intervention_time = interventiontime) %>% 
  select(home_winter_id, home_id, winter_id, intervention_date, intervention_time)

@@

kids_ids <- rbind(ak_ids, nn_ids, wmt_ids) %>% 
  mutate(home = gsub("_", "", home)) %>% 
  mutate(home = gsub("-", "", home)) %>% 
  mutate(home = gsub(" ", "", home)) %>% 
  mutate(home_id = as.numeric(home_id)) %>% 
  filter(home_id < 1000) %>%  
  mutate(home_id = as.character(home_id)) %>% 
  # distinct(area, home_id)  # enrolled homes in database = 360
  filter(!is.na(treatment)) %>% 
  filter(winter_id != 99) %>% 
  # distinct(area, home_id)  # randomized homes with treatment assignment = 342
  ### WMA222 and WMA 233 had a treatment but no kids - not counting in flow chart
  filter(home != "WMA222" & home != "WMA233") %>% 
  #distinct(area, home_id)  # randomized homes with treatment assignment = 340
  ungroup() %>% 
  arrange(area, home)

@@

# Checking observations against drop reasons from "KidsAIR reasons for dropping" excel file
# Filter out observations below when participants had dropped and should not be in dataset
demographics_check <- demographics_initial %>% 
  filter(area == "AK") %>% 
  arrange(home, child_id_char)

# dropped before winter 1 - filter out
filter_out_wmt <- c("WMA227", "WMA254", "WMA337", "WMA600", "WMA601")
# missing winter 2 demographic data but had not dropped - don't filter out
keep_winter_2_wmt <- c("WMA407", "WMA497", "WMA509")
# NN homes with missing data but had not dropped - don't filter out
keep_nn <- c("CH110", "TC359", "TC452", "TC453")

demographics_new <- demographics_initial %>% 
  filter(!home %in% filter_out_wmt) %>% 
  mutate(keep_var_wmt = if_else(home %in% keep_winter_2_wmt & winter_id == 2, 1, 0),
         filter_var_wmt = if_else(area == "WMT" & keep_var_wmt == 0 & winter_id == 2 & is.na(gender_parent), 1, 0)) %>% 
  filter(filter_var_wmt == 0) %>% 
  filter(home != "CH105") %>% 
  mutate(keep_var_nn = if_else(home %in% keep_nn, 1, 0),
         filter_var_nn = if_else(area == "NN" & keep_var_nn == 0 & is.na(gender_parent), 1, 0)) %>% 
  filter(filter_var_nn == 0) %>% 
  filter(home != "YKC19102") %>% 
  filter(home != "YKC19104") %>% 
  mutate(filter_var_ak = if_else(area == "AK" & is.na(gender_parent), 1, 0)) %>% 
  filter(filter_var_ak == 0) %>%
  mutate(treatment_assigned = as.character(treatment),
         treatment_actual = as.character(treatment),
         treatment_assigned = if_else(treatment == "Placebo - TX Education", "Placebo", treatment_actual)) %>% 
  select(-treatment, -filter_var_wmt, -keep_var_wmt, -filter_var_nn, 
         -keep_var_nn, -filter_var_ak)

@@

>>>>

## Box location: All Files > NoonGroupData > KidsAIR > 
## FINAL DATA SETS > WMT > homewinter
wmt_homewinter_initial <- read_csv(paste0(file_path, "Input/WMT/homewinter.csv"), na = "NULL") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, homeid, winterid, interventiondate, interventiontime) %>% 
  filter(winterid == 1 | winterid ==2) %>% # filter for winterid == 1 or 2. What about missing intervention date?
  mutate(home_winter_id = as.character(homewinterid),
         home_id = as.character(homeid),
         winter_id = as.character(winterid),
         intervention_date = interventiondate,
         intervention_time = interventiontime) %>% 
  select(home_winter_id, home_id, winter_id, intervention_date, intervention_time)

@@

## Box location: All Files > NoonGroupData > KidsAIR > 
## FINAL DATA SETS > Navajo > homewinter
nn_homewinter_initial <- read_csv(paste0(file_path, "Input/NN/homewinter.csv"), na = "NULL") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, homeid, winterid, interventiondate, interventiontime) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         home_id = as.character(homeid),
         winter_id = as.character(winterid),
         intervention_date = interventiondate,
         intervention_time = interventiontime) %>% 
  mutate(winter_id = as.numeric(winter_id),
         winter_id = as.character(winter_id)) %>% 
  filter(winter_id == 0 | winter_id == 1 | winter_id ==2) %>% # filter for winterid == 1 or 2. What about missing intervention date?
  select(home_winter_id, home_id, winter_id, intervention_date, intervention_time)

@@

## Box location: All Files > NoonGroupData > KidsAIR > 
## FINAL DATA SETS > AK > homewinter
ak_homewinter_initial <- read_csv(paste0(file_path, "Input/AK/homewinter.csv"), na = "NULL") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, homeid, winterid, interventiondate, interventiontime) %>% 
  filter(winterid == 1 | winterid ==2) %>% # filter for winterid == 1 or 2. What about missing intervention date?
  mutate(home_winter_id = as.character(homewinterid),
         home_id = as.character(homeid),
         winter_id = as.character(winterid),
         intervention_date = interventiondate,
         intervention_time = interventiontime) %>% 
  select(home_winter_id, home_id, winter_id, intervention_date, intervention_time)

@@

kids_ids <- rbind(ak_ids, nn_ids, wmt_ids) %>% 
  mutate(home = gsub("_", "", home)) %>% 
  mutate(home = gsub("-", "", home)) %>% 
  mutate(home = gsub(" ", "", home)) %>% 
  mutate(home_id = as.numeric(home_id)) %>% 
  filter(home_id < 1000) %>%  
  mutate(home_id = as.character(home_id)) %>% 
  # distinct(area, home_id)  # enrolled homes in database = 360
  filter(!is.na(treatment)) %>% 
  # distinct(area, home_id)  # randomized homes with treatment assignment = 342
  ### WMA222 and WMA 233 had a treatment but no kids - not counting in flow chart
  filter(home != "WMA222" & home != "WMA233") %>% 
  #distinct(area, home_id)  # randomized homes with treatment assignment = 340
  ungroup() %>% 
  arrange(area, home)

@@

# Checking observations against drop reasons from "KidsAIR reasons for dropping" excel file
# Filter out observations below when participants had dropped and should not be in dataset
demographics_check <- demographics_initial %>% 
  filter(area == "NN") %>% 
  arrange(home, child_id_char)

# dropped before winter 1 - filter out
filter_out_wmt <- c("WMA227", "WMA254", "WMA337", "WMA600", "WMA601")
# missing winter 2 demographic data but had not dropped - don't filter out
keep_winter_2_wmt <- c("WMA407", "WMA497", "WMA509")
# NN homes with missing data but had not dropped - don't filter out
keep_nn <- c("CH110", "CH209", "TC359", "TC452", "TC453")

demographics_new <- demographics_initial %>% 
  filter(!home %in% filter_out_wmt) %>% 
  mutate(keep_var_wmt = if_else(home %in% keep_winter_2_wmt & winter_id == 2, 1, 0),
         filter_var_wmt = if_else(area == "WMT" & keep_var_wmt == 0 & winter_id == 2 & is.na(gender_parent), 1, 0)) %>% 
  filter(filter_var_wmt == 0) %>% 
  filter(home != "CH105") %>% 
  mutate(keep_var_nn = if_else(home %in% keep_nn, 1, 0),
         filter_var_nn = if_else(area == "NN" & keep_var_nn == 0 & is.na(gender_parent), 1, 0)) %>% 
  filter(filter_var_nn == 0) %>% 
  mutate(filter_var_nn = if_else(home == "CH209" & winter_id == 2, 1, 0)) %>% 
  filter(filter_var_nn == 0) %>% 
  filter(home != "YKC19102") %>% 
  filter(home != "YKC19104") %>% 
  mutate(filter_var_ak = if_else(area == "AK" & is.na(gender_parent), 1, 0)) %>% 
  filter(filter_var_ak == 0) %>%
  mutate(treatment_assigned = as.character(treatment),
         treatment_actual = as.character(treatment),
         treatment_assigned = if_else(treatment == "Placebo - TX Education", "Placebo", treatment_actual),
         winter_id = as.factor(winter_id),
         treatment_assigned = as.factor(treatment_assigned),
         treatment_actual = as.factor(treatment_actual),
         area = as.factor(area)) %>% 
  select(-treatment, -filter_var_wmt, -keep_var_wmt, -filter_var_nn, 
         -keep_var_nn, -filter_var_ak)

@@

# Final check for home and child observations by winter and treatment
```{r}
kids_linked_ids <- read_rds(paste0(file_path, "Output/kids_linked_ids_final.rds")) %>% 
  count(area, winter_id, treatment_assigned)

demographics <- read_rds(paste0(file_path, "Output/demographics_final.rds")) %>% 
  count(area, winter_id, treatment_assigned)
```

### 2020-06-19 indoor_temp_rh_summary.Rmd
new data cleaning/merging

```{r}
# Load data
indoor_temp_rh_clean <- read_rds("Output/indoor_temp_rh_clean.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")
pm_clean <- read_rds("Output/pm_clean.rds")
```

>>>>

```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")
# Load data
kids_linked_ids <- read_rds(paste0(file_path, "Output/kids_linked_ids_final.rds")) 
demographics <- read_rds(paste0(file_path, "Output/demographics_final.rds")) 
pm_clean <- read_rds(paste0(file_path, "Output/pm_clean.rds"))
```

### 2020-06-19 manuscript_tables_figures.Rmd
new data cleaning/merging

kids_linked_ids <- read_rds(paste0(file_path, "Output/kids_linked_ids.rds"))

demographics_initial <- read_rds(paste0(file_path, "Output/demographics_clean.rds"))

>>>>

kids_linked_ids <- read_rds(paste0(file_path, "Output/kids_linked_ids_final.rds"))

demographics <- read_rds(paste0(file_path, "Output/demographics_final.rds"))
